%=====================================================================
%  RAHUL NAHATA — RESUME (SINGLE-COLUMN, ATS-HARDENED)
%  Compile with: XeLaTeX (recommended) or pdfLaTeX
%  Overleaf: Menu → Settings → Compiler → XeLaTeX
%
%  This variant is optimised for Applicant Tracking Systems:
%  - Single-column, strict top-to-bottom reading order
%  - Standard section headings (Summary, Experience, Skills, etc.)
%  - No icons, no tables, no text boxes, no multi-column layouts
%  - Comma-separated keyword lists (tokenise cleanly)
%  - Plain text contact line (no font glyphs)
%  - Subtle orange accent retained for human readability
%=====================================================================
\documentclass[9pt,a4paper]{extarticle}

%---------- FONTS ----------
\usepackage{iftex}
\ifxetex
  \usepackage{fontspec}
  \IfFontExistsTF{Inter}{%
    \setmainfont{Inter}[
      UprightFont    = * Regular,
      BoldFont       = * SemiBold,
      ItalicFont     = * Italic,
      BoldItalicFont = * SemiBold Italic
    ]
  }{%
    \setmainfont{Latin Modern Sans}
  }
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
  \renewcommand{\familydefault}{\sfdefault}
\fi

%---------- PAGE / LAYOUT ----------
\usepackage[a4paper,top=0.8cm,bottom=0.8cm,left=1.1cm,right=1.1cm]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\setlength{\parskip}{0.5pt plus 0.3pt}
\linespread{0.98}

%---------- COLORS (subtle; ATS ignores colour) ----------
\definecolor{accent}{HTML}{FF9900}
\definecolor{textdark}{HTML}{1A1A1A}
\definecolor{textmuted}{HTML}{555555}
\color{textdark}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent,
  pdftitle={Rahul Nahata - Resume},
  pdfauthor={Rahul Nahata},
  pdfsubject={Software Development Manager Resume},
  pdfkeywords={Software Development Manager, Engineering Leader, FinTech, Compliance, AWS, Java, Distributed Systems, Amazon}
}

%---------- SECTION ----------
\newcommand{\cvsection}[1]{%
  \vspace{2pt}%
  {\normalsize\bfseries\color{textdark}\MakeUppercase{#1}}\par
  \vspace{-1pt}%
  {\color{accent}\rule{\linewidth}{0.6pt}}\par
  \vspace{0pt}%
}

\setlist[itemize]{
  leftmargin=1.1em,
  topsep=0pt,
  itemsep=0pt,
  parsep=0pt,
  label=\textbullet
}

%---------- ROLE HEADING ----------
% Real text, no decorative glyphs — fully parseable.
\newcommand{\role}[4]{%
  \textbf{#1} \hfill \textbf{#4}\par
  \textit{#2, #3}\par\vspace{0pt}
}

\newcommand{\edublock}[4]{%
  \textbf{#1} \hfill \textbf{#4}\par
  \textit{#2} -- #3\par\vspace{0pt}
}

%=====================================================================
\begin{document}
\pagestyle{empty}
\setlength{\parindent}{0pt}

%---------- HEADER (plain text, ATS-safe) ----------
\begin{center}
  {\fontsize{18pt}{20pt}\selectfont\bfseries Rahul Nahata}\\[0pt]
  {\small Software Development Manager, Amazon}\\[0pt]
  {\scriptsize Ghaziabad, India ~|~ +91 70425 22288 ~|~
   \href{mailto:rahulnahata@hotmail.co.in}{rahulnahata@hotmail.co.in} ~|~
   \href{https://linkedin.com/in/rahulnahata05}{linkedin.com/in/rahulnahata05} ~|~
   \href{https://nahatarahul.github.io}{nahatarahul.github.io}}
\end{center}
\vspace{0pt}
{\color{accent}\rule{\linewidth}{0.7pt}}

\small

%---------- SUMMARY ----------
\cvsection{Professional Summary}
Engineering leader with \textbf{13+ years} building large-scale systems across FinTech,
tax compliance, and revenue protection. Currently leading global teams at Amazon focused
on preventing financial losses across millions of transactions worldwide. Deep hands-on
background as a Software Development Engineer across withholding tax automation, global
compliance reporting, and EDA tooling. Experienced in leading distributed teams across
India and Europe, defining engineering roadmaps, and partnering with Finance, Legal, Tax,
and Compliance stakeholders.

%---------- CORE SKILLS (keyword-dense block for ATS) ----------
\cvsection{Core Skills}
\textbf{Leadership:} Software Development Management, People Management, Team Building,
Global Stakeholder Management, Technical Roadmap, Strategy, Engineering Excellence,
Bar Raising, Hiring, Organisational Design, Cross-functional Collaboration.\par\vspace{2pt}
\textbf{Technical:} Java, C, C++, Python, R, Matlab, Shell, Distributed Systems,
AWS Cloud Infrastructure, Linux, Large-scale Backend Services, Microservices, REST APIs,
SQL, Oracle, Data Structures, Algorithms, Computer Networks, System Design.\par\vspace{2pt}
\textbf{Domains:} FinTech, Withholding Tax, Global Compliance Reporting, Tax Automation,
Regulatory Technology, Fraud and Abuse Prevention, Revenue Protection, EDA Tools,
Production Engineering.\par\vspace{2pt}
\textbf{AI and Emerging Tech:} Generative AI for Leaders, Agentic AI, CrewAI, LangGraph,
Zapier, Amazon Bedrock, AI Automation, Workflow Automation, Blockchain, Smart Contracts.

%---------- EXPERIENCE ----------
\cvsection{Professional Experience}

\role{Software Development Manager, NCRC (Revenue Protection)}{Amazon}{Gurugram, India}{August 2025 -- Present}
\begin{itemize}
  \item Leading global engineering teams to reduce Amazon's Net Cost of Refunds and
        Concessions, protecting millions of transactions worldwide.
  \item Building intelligent systems that distinguish genuine customer issues from
        systematic fraud and abuse at massive scale.
  \item Owning engineering roadmap, hiring, and organisational health across multiple
        geographies.
\end{itemize}

\role{Software Development Manager, FinTech (Global Compliance)}{Amazon}{Gurugram, India}{July 2024 -- August 2025}
\begin{itemize}
  \item Led global FinTech engineering teams across India and Europe delivering
        compliance systems under strict regulatory deadlines.
  \item Defined engineering roadmap, drove team health across geographies, and
        partnered with Finance, Legal, Tax, and Compliance stakeholders.
\end{itemize}

\role{Software Development Engineer III, FinTech Compliance Reporting}{Amazon}{Gurugram, India}{December 2022 -- July 2024}
\begin{itemize}
  \item Designed and built a modular, plug-and-play compliance reporting platform
        enabling automated regulatory filings across multiple countries.
  \item Architected the platform so new jurisdictions could onboard without rebuilding
        from scratch, significantly reducing delivery time for new regulatory
        requirements.
\end{itemize}

\role{Software Development Engineer II, FinTech Withholding Tax}{Amazon}{Gurugram, India}{August 2019 -- December 2022}
\begin{itemize}
  \item Owned Amazon's global withholding tax product including automated tax
        deductions at source, government disbursements, and customer refund mechanisms.
  \item Delivered across multiple geographies with strict correctness and auditability
        requirements.
\end{itemize}

\role{Software Engineer II}{Cadence Design Systems}{Noida, India}{November 2017 -- August 2019}
\begin{itemize}
  \item As part of the Cadence R\&D team, worked on Xcelium parallel logic simulator
        software, specifically on coverage testing and automations used to design
        next-generation intelligent systems on chip.
\end{itemize}

\role{Lead Engineer}{Samsung India Electronics}{Noida, India}{July 2013 -- November 2017}
\begin{itemize}
  \item Part of Commercial R\&D team. Built tools and automation for production
        testing, Android platform validation, and RF calibration workflows.
  \item Built a real-time log analysis tool with predictive issue detection, OS
        upgrade validation automation, and an SMP-based binary download optimisation
        delivering significant factory throughput improvement.
\end{itemize}

%---------- EDUCATION ----------
\cvsection{Education}
\edublock{Bachelor of Technology, Computer Science and Engineering}{Indian Institute of Technology, Jodhpur}{CGPA 8.82 / 10, IIT JEE AIR 2813 among 384,977 candidates}{2009 -- 2013}
\edublock{Class XII, Science (CBSE)}{Aklank Public School, Rajasthan}{84.5\%}{2006 -- 2008}

%---------- CERTIFICATIONS ----------
\cvsection{Certifications}
\begin{itemize}
  \item ChatGPT and Zapier: Agentic AI for Everyone, Vanderbilt University, October 2025
  \item Generative AI Automation Tools, Edureka, September 2025
  \item Generative AI for Leaders, Vanderbilt University, August 2025
  \item Smart Contracts, Coursera, March 2019
  \item Blockchain Basics, Coursera, February 2019
\end{itemize}

%---------- INTERNSHIPS ----------
\cvsection{Internships}
\begin{itemize}
  \item \textbf{National Instruments, India} -- Technical Marketing Intern, Bengaluru
        (May 2012 -- July 2012).
  \item \textbf{University of Technology of Troyes, France} -- R\&D Intern, CAPSEC
        Research Programme, Troyes (May 2011 -- July 2011).
\end{itemize}

\end{document}
